---
title: "Lab 08 - University of Edinburgh Art Collection"
author: "Fiona Wang"
date: "03-04-2025"
output: github_document
---

## Load Packages and Data  

First, let's load the necessary packages:  

```{r load-packages, message = FALSE}
library(tidyverse) 
library(skimr)
library(scales)
```

Now, load the dataset. If your data isn't ready yet, you can leave `eval = FALSE` for now and update it when needed.  


```{r load-data, message = FALSE}
# Remove eval = FALSE or set it to TRUE once data is ready to be loaded
uoe_art <- read_csv("data/uoe-art.csv")
```

## Exercise 9

Let's start working with the **title** column by separating the title and the date:  

```{r separate-title-date, error = TRUE}
uoe_art <- uoe_art %>%
  separate(title, into = c("title", "date"), sep = "\\(") %>%
  mutate(year = str_remove(date, "\\)") %>% as.numeric()) %>% 
  select(title, artist, year, link)  # Fill in the missing variable!
```

The warning message means that R didn't identify a ")" in the title, so they put NA in the year column for those instances.      
Some had month info which we don't need. Using the as.numeric changed those instances to NAs. We lost some information in this process. 

## Exercise 10  
```{r artistunknown}
uoe_art <- uoe_art %>% 
  mutate(artist = ifelse(artist == "Unknown", NA, artist))
```

Here, I changed the artist column. I observed that a lot of artists are unknown, but they are written as unknown and not NA. I changed them into NAs, so that the next question will have a more accurate answer. 

## Exercise 11  
```{r skim}
skim(uoe_art)
```
We are missing 484 pieces of artist info. We are missing 1580 pieces of year info. 

## Exercise 12
```{r plot}
uoe_art %>% 
  ggplot(aes(x = year)) +
  geom_histogram(binwidth = 1) 
```

To be honest, I didn't see anything unusual at first. Later, when scrolling through the data frame, I realized that there is something unusual. There is a year which is close to zero. On the graph here, it's almost invisible. 

## Exercise 13
```{r findunusual}
unusual <- uoe_art %>% 
  filter(year < 500)
```
We found the outlier. It is published in the year 2. Looking it up online, the correct year is actually 1964. The title is Death Mask(2), this parentheses is the reason why R coded this piece as year 2. 

```{r correction}
uoe_art <- uoe_art %>% 
  mutate(year = case_when(
    year == 2 ~ 1964,
    TRUE ~ year
  ))
```
```{r plotagain, warning = FALSE}
uoe_art %>% 
  ggplot(aes(x = year)) +
  geom_histogram(binwidth = 1)
```

## Exercise 14
```{r top1artist}
uoe_art %>% 
  count(artist) %>% 
  arrange(desc(n))
```

Apart from NAs, Emma Gillies appears the most commonly featured artist in the collection. I don't know this person. The way that the question is asked, I would guess that this person is a professor or previous student from this university. 

## Exercise 15
```{r child}
uoe_art %>% 
  filter(str_detect(title, "child|Child"))
```

There are 11 pieces that have the word "child" in their title. 
